---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinyLottie

<!-- badges: start -->

<!-- badges: end -->

The shinyLottie package allows users to easily integrate and control Lottie animations within Shiny applications, without the need for idiosyncratic expression or use of JavaScript. This includes utilities for generating animation instances, controlling playback, manipulating animation properties, and more.

## Installation

You can install the development version of shinyLottie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CamHowitt/shinyLottie")
```

## Example

Introducing Lottie animations to a Shiny app can be accomplished using just two shinyLottie functions:

```{r eval = FALSE}
library(shiny)
library(shinyLottie)

ui <- fluidPage(
  include_lottie(),
  lottie_animation(
    path = "shinyLottie/example.json",
    name = "my_animation"
  )
)

server <- function(input, output, session) {}

shinyApp(ui, server)
```

For more advanced implementations, please refer to the following articles:

-   `vignette("shinyLottie")`

-   `vignette("Controlling-Animations")`

-   `vignette("Event-Listeners")`
